I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-11-30 paper_io_sim.tex
Update README, source code url

			In this work, we use Python 3.7 to implement the single-threaded simulator, 
			SimGrid 3.25 and WRENCH 1.6 for more multi-threaded simulators. 
			SimGrid source code is available at \url{https://framagit.org/simgrid/simgrid}, 
			and WRENCH is at \url{https://github.com/dohoangdzung/wrench/tree/io_nfs} 	
			\textcolor{red}{Update later with the commit used in the simulator}

@@

			In simulated platform description, because the disk bandwidths in SimGrid 
			are symmetrical, we measure the read/write bandwidths on our cluster and 
			take the average bandwidths. 
			As the pipelines are single-core, we create simulated tasks, 
			each of them runs on only one core. 
			While in Python, computation time can be directly configured, 
			this time is injected to the WRENCH simulators with number of flops, 
			which is calculated with CPU speed and compute duration. 
			In our experiments, the CPU speed is set to 1 Gflops. 
			Finally, because WRENCH simulates applications base on network-communication, 
			we use an infinite bandwidth to eliminate network latency for local I/Os.
			The details of simulated platform is available here: 
			\url{https://github.com/dohoangdzung/wrench/blob/io_chunk_test/examples/basic-examples/io-pagecache/single_host.xml}

>>>>

			In this work, we use Python 3.7 to implement the single-threaded simulator, 
			SimGrid 3.25 and WRENCH 1.6 for more multi-threaded simulators. 
			SimGrid source code is available at \url{https://framagit.org/simgrid/simgrid}, 
			and WRENCH is at 
			\url{https://github.com/wrench-project/wrench/tree/master/src/wrench/services/memory}.

@@

			In simulated platform description, because the disk bandwidths in SimGrid 
			are symmetrical, we measure the read/write bandwidths on our cluster and 
			take the average bandwidths. 
			As the pipelines are single-core, we create simulated tasks, 
			each of them runs on only one core. 
			While in Python, computation time can be directly configured, 
			this time is injected to the WRENCH simulators with number of flops, 
			which is calculated with CPU speed and compute duration. 
			In our experiments, the CPU speed is set to 1 Gflops. 
			Finally, because WRENCH simulates applications base on network-communication, 
			we use an infinite bandwidth to eliminate network latency for local I/Os.
			The details of simulated platform and the source code of the simulator 
			are available here: 
			\url{https://github.com/wrench-project/wrench/tree/master/examples/basic-examples/io-pagecache}
